Estimating the dynamics of SPARQL query results

### 2019-04-11 kgswc19.tex
update

\begin{figure}[!t]
	\caption{Top-10 dynamic predicates according with total (left) and proportional (right) changes}
	\label{tab:predicates}
	\resizebox{0.45\textwidth}{!}{
		\begin{tabular}{rlrr}    \toprule
			\ntextnumero        & Predicate & Total	& Dyn 	\\  \midrule
			1 & schema:description  & 464567354  	& 0.04   \\
			2 & schema:dateModified  & 99330382  	& 0.14   \\
			3 & schema:version  & 99330164  	& 0.14  \\
			4 & schema:name  & 44487864  	& 0.01   \\
			5 & rdfs:label  & 44487864  	& 0.01   \\
			6 & skos:prefLabel  & 44487864  	& 0.01   \\
			7 & wdt:P2093(author name)  & 30671685  	& 0.09   \\
			8 & rdf:type  & 21808957  	& 0.02   \\
			9 & wdt:P31(instance of)  & 12483471  	& 0.02   \\
			10 & schema:about  & 10773295  	& 0.02  \\    \bottomrule
		\end{tabular}	
	}
	\hfill
	\resizebox{0.5\textwidth}{!}{
		\begin{tabular}{rlrr}    \toprule
			\ntextnumero        & Predicate & Total	& Dyn 	\\  \midrule
			1 & owl:complementOf & 156862 & 0.99	\\
			2 & owl:onProperty & 156862 & 0.99	\\
			3 & owl:someValuesFrom & 86674 & 0.71	\\
			4 & wdt:P2462(member of the deme) & 3563 & 0.62	\\
			5 & wdt:P3383(film poster) & 4388 & 0.58	\\
			6 & wdt:P2331(Cycling Archives ID) & 4229 & 0.33	\\
			7 & wdt:P1112() & 4366 & 0.20	\\
			8 & wdt:P505(general manager) & 4959 & 0.18	\\
			9 & schema:dateModified & 99330382 & 0.14	\\
			10 & schema:version & 99330164 & 0.14	\\    \bottomrule
		\end{tabular}	
	}	
\end{figure}

@@

\begin{table}[t]
	\begin{minipage}[b]{0.47\linewidth}
		\centering
		\caption{Distribution of triple patterns (C: Constant, V: Variable, P: Path). \label{tab:Pattern}}
		\begin{tabular}{lrr}    \toprule
			\textbf{Pattern} & \textbf{\ntextnumero} & \textbf{\%} \\    \midrule
			V C V   & 435      & 59.43\%    \\
			V C C   & 190      & 25.96\%    \\
			V V V   & 9        & 1.23\%     \\
			C C V   & 6        & 0.82\%     \\
			V V C   & 5        & 0.68\%     \\
			C V V   & 3        & 0.41\%     \\
			C V C   & 1        & 0.14\%     \\
			C C C   & 0        & 0.00\%     \\    \midrule
			V P C   & 69       & 9.43\%     \\
			V P V   & 13       & 1.78\%     \\
			C P V   & 1        & 0.14\%     \\
			C P C   & 0        & 0.00\%     \\    \bottomrule
		\end{tabular}
	\end{minipage}
	\hfill
	\begin{minipage}[b]{0.47\linewidth}
		\centering
		\caption{Distribution of paths\label{tab:Path}}
		\begin{tabular}{lrr}    \toprule
			\textbf{Pattern}      & \textbf{\ntextnumero} & \textbf{\%} \\    \midrule
			$e\texttt{*}$   & 62       & 74.70\%     \\
			$e_1 \texttt{/} e_2$  & 56       & 67.47\%    \\
			$e\texttt{+} $   & 8        & 9.64\%     \\
			$e_1 \texttt{|} e_2$  & 6        & 7.23\%     \\
			$e\texttt{?}$    & 6        & 7.23\%     \\
			$\texttt{!(}e\texttt{)}$ & 0        & 0.00\%        \\ \midrule
			$e$ & 83 & 100.00\% \\
			\bottomrule
		%	$P \rightarrow C $    & 83       & 100.00\%      \\    \bottomrule
		\end{tabular}
	\end{minipage}
\end{table}

@@

Furthermore, we show in Figure~\ref{fig:result} that effectively the size of the window influences the quality of the results when considering \textsc{r}, being better as the window increases. However, these results are not affected when we consider only predicates in \textsc{q} or  \textsc{p}. Also, we show, that all configurations outperform the random baseline.

>>>>

\begin{figure}[!t]
	\caption{Top-10 dynamic predicates according with total (left) and proportional (right) changes}
	\label{tab:predicates}
	\resizebox{0.45\textwidth}{!}{
		\begin{tabular}{r@{\hskip 0.1in}lr@{\hskip 0.1in}r}    \toprule
			\ntextnumero        & Predicate & Total	& Dyn 	\\  \midrule
			1 & schema:description  & 464567354  	& 0.04   \\
			2 & schema:dateModified  & 99330382  	& 0.14   \\
			3 & schema:version  & 99330164  	& 0.14  \\
			4 & schema:name  & 44487864  	& 0.01   \\
			5 & rdfs:label  & 44487864  	& 0.01   \\
			6 & skos:prefLabel  & 44487864  	& 0.01   \\
			7 & wdt:P2093(author name)  & 30671685  	& 0.09   \\
			8 & rdf:type  & 21808957  	& 0.02   \\
			9 & wdt:P31(instance of)  & 12483471  	& 0.02   \\
			10 & schema:about  & 10773295  	& 0.02  \\    \bottomrule
		\end{tabular}	
	}
	\hfill
	\resizebox{0.5\textwidth}{!}{
		\begin{tabular}{r@{\hskip 0.1in}lr@{\hskip 0.1in}r}    \toprule
			\ntextnumero        & Predicate & Total	& Dyn 	\\  \midrule
			1 & owl:complementOf & 156862 & 0.99	\\
			2 & owl:onProperty & 156862 & 0.99	\\
			3 & owl:someValuesFrom & 86674 & 0.71	\\
			4 & wdt:P2462(member of the deme) & 3563 & 0.62	\\
			5 & wdt:P3383(film poster) & 4388 & 0.58	\\
			6 & wdt:P2331(Cycling Archives ID) & 4229 & 0.33	\\
			7 & wdt:P1112() & 4366 & 0.20	\\
			8 & wdt:P505(general manager) & 4959 & 0.18	\\
			9 & schema:dateModified & 99330382 & 0.14	\\
			10 & schema:version & 99330164 & 0.14	\\    \bottomrule
		\end{tabular}	
	}	
\end{figure}

@@

\begin{table}[t]
	\begin{minipage}[b]{0.47\linewidth}
		\centering
		\caption{Distribution of triple patterns (C: Constant, V: Variable, P: Path). \label{tab:Pattern}}
		\begin{tabular}{l@{\hskip 0.2in}r@{\hskip 0.2in}r}    \toprule
			\textbf{Pattern} & \textbf{\ntextnumero} & \textbf{\%} \\    \midrule
			V C V   & 435      & 59.43\%    \\
			V C C   & 190      & 25.96\%    \\
			V V V   & 9        & 1.23\%     \\
			C C V   & 6        & 0.82\%     \\
			V V C   & 5        & 0.68\%     \\
			C V V   & 3        & 0.41\%     \\
			C V C   & 1        & 0.14\%     \\
			C C C   & 0        & 0.00\%     \\    \midrule
			V P C   & 69       & 9.43\%     \\
			V P V   & 13       & 1.78\%     \\
			C P V   & 1        & 0.14\%     \\
			C P C   & 0        & 0.00\%     \\    \bottomrule
		\end{tabular}
	\end{minipage}
	\hfill
	\begin{minipage}[b]{0.47\linewidth}
		\centering
		\caption{Distribution of paths\label{tab:Path}}
		\begin{tabular}{l@{\hskip 0.2in}r@{\hskip 0.2in}r}    \toprule
			\textbf{Pattern}      & \textbf{\ntextnumero} & \textbf{\%} \\    \midrule
			$e\texttt{*}$   & 62       & 74.70\%     \\
			$e_1 \texttt{/} e_2$  & 56       & 67.47\%    \\
			$e\texttt{+} $   & 8        & 9.64\%     \\
			$e_1 \texttt{|} e_2$  & 6        & 7.23\%     \\
			$e\texttt{?}$    & 6        & 7.23\%     \\
			$\texttt{!(}e\texttt{)}$ & 0        & 0.00\%        \\ \midrule
			$e$ & 83 & 100.00\% \\
			\bottomrule
		%	$P \rightarrow C $    & 83       & 100.00\%      \\    \bottomrule
		\end{tabular}
	\end{minipage}
\end{table}

@@

Furthermore, we show in Figure~\ref{fig:result} that effectively the size of the window influences the quality of the results when considering \textsc{r} (blue), being better as the window increases. However, these results are not affected when we consider only predicates in \textsc{q} (brown), \textsc{p} (green)  or \textsc{qp} (black). Also, we show, that all configurations outperform the random baseline (red).
